Analytical reproducibility and data reusability of published meta-analyses on clinical psychological interventions

### 2022-11-17 manuscript.Rmd
minor corrections in manuscript

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these as well as the required elements to be able to reproduce each stage.

@@

@@

## Reproducibility checks workflow 
Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment [@r2022] using the *metafor* package [@viechtbauer2010]. The scripts are available at: ….

@@

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`). Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: …

@@

## Acknowledgments 
We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript. We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in step 3.

@@

# Supplemental Material

# Prior versions

>>>>

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as the required elements to be able to reproduce each stage.

@@

Data and analysis script code are openly available at: https://osf.io/6cmzh/

@@

## Reproducibility checks workflow 
Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment [@r2022] using the *metafor* package [@viechtbauer2010].

@@

From the 100 included papers, `r n_mas_total` independent meta-analyses were selected following the criteria explained above. These meta-analyses included `r round(k_mean, 2)` primary studies on average (`r sprintf("sd = %0.2f; median = %0.0f; interquartile range = %0.0f-%0.0f; range = %0.0f-%0.0f)", k_sd, k_median, k_q1, k_q3, range[1], range[2])`). Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: https://osf.io/8jzbk

@@

## Acknowledgments 
We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript. We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in the third stage.

@@

## Supplemental Material

## Prior versions

### 2022-11-17 manuscript.tex
minor corrections in manuscript

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability (López-Nicolás et al., 2022; Polanin et al., 2020). Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009) possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these as well as the required elements to be able to reproduce each stage.

@@

@@

Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment (R Core Team, 2022) using the \emph{metafor} package (Viechtbauer, 2010). The scripts are available at: \ldots.

@@

From the 100 included papers, 217 independent meta-analyses were selected following the criteria explained above. These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134)). Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: \ldots{}

@@

We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript. We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in step 3.

@@

\hypertarget{supplemental-material}{%
\section{Supplemental Material}\label{supplemental-material}}

\hypertarget{prior-versions}{%
\section{Prior versions}\label{prior-versions}}

>>>>

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability (López-Nicolás et al., 2022; Polanin et al., 2020). Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies (Gøtzsche et al., 2007; Maassen et al., 2020; Tendal et al., 2009) possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as the required elements to be able to reproduce each stage.

@@

Data and analysis script code are openly available at: \url{https://osf.io/6cmzh/}

@@

Analytical reproducibility checks were carried out at different stages. First, through reported analytic details or script code. When the analysis script code was available, computational reproducibility was checked by rerunning the script with the available primary data. In most cases, the analysis script code was not available. Thus, in these cases we coded the analytic details as explained above to fit equivalent meta-analytic models as a function of these details using the available primary data. This analysis scheme was programmed in the R environment (R Core Team, 2022) using the \emph{metafor} package (Viechtbauer, 2010).

@@

From the 100 included papers, 217 independent meta-analyses were selected following the criteria explained above. These meta-analyses included 18.35 primary studies on average (sd = 17.25; median = 13; interquartile range = 10-19; range = 3-134)). Figure 2 displays the distribution of number of primary studies among the meta-analyses included in our sample. Original results and characteristics of these meta-analyses are available at: \url{https://osf.io/8jzbk}

@@

We thank the research group of the Meta-Research Centre of Tilburg University for providing feedback on an earlier version of this manuscript. We would also like to thank all the original authors of the included meta-analyses who enabled access to the data used in this project as well as the authors who provided clarifications in response to requests for clarification in the third stage.

@@

\hypertarget{supplemental-material}{%
\subsection{Supplemental Material}\label{supplemental-material}}

\hypertarget{prior-versions}{%
\subsection{Prior versions}\label{prior-versions}}
